PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-15 paper/ms.tex
minor word smithing

\keywords{
	Exoplanet evolution (491),
  Pre-main sequence stars (1290),
	Stellar ages (1581),
	Stellar rotation (1629),
	Variable stars (1761),
  Low mass stars (2050)
}

@@

With the Gaia astrometry, it has become clear that 25$\,$Ori itself
has distinct subgroups
\citep{kounkel_apogee2_2018,briceno_cidaII_2019}.  In describing the
cluster membership of \ptfo, we follow the notation and results of
\citet{kounkel_apogee2_2018}.  These authors combined astrometric data
from Gaia DR2 with near-infrared spectra from APOGEE-2
\citep{gunn_sdss_2006,majewski_apache_2017,blanton_sloan_2017,zasowski_target_2017,cottle_apogee2_2018}.
They performed a hierarchical clustering on the six-dimensional
position and velocity information to identify subgroups within the
Orion complex.  From smallest to largest, \ptfo\ was identified as a
member of the following hierarchical subgroups:
\begin{equation}
  {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where `$\subset$' means `is a proper subset of'.  25$\,$Ori-1 is the
largest subgroup of 25$\,$Ori, with 149 identified members.  The mean
age of the 25$\,$Ori-1 subgroup, determined by fitting isochrones to
group members that had effective temperatures from APOGEE and Gaia
parallaxes, was determined to be $8.5\pm1.2\,{\rm Myr}$
\citep[see][Section 2.3]{kounkel_apogee2_2018}.
\citet{kounkel_apogee2_2018} identified seven other smaller groups in
the Orion complex near the Be star 25$\,$Ori. These groups received
sequential identifiers, {\it e.g.}, 25$\,$Ori-2 (${\rm Age}
=12.9\pm2.8\,$Myr; see also \citealt{briceno_cidaII_2019}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: The longer-period signal.  {\it Bottom}: The
    shorter-period signal. The phase is defined such that the dip
    occurs at zero phase.  Gray points are the \texttt{PDCSAP} data
    binned to 10-minute cadence.  Black points are binned to 100
    points per period.  The model (blue line) includes 2 harmonics at
    the longer period, plus 3 harmonics and a transit at the shorter
    period.
		\label{fig:phasefold}
	}
\end{figure*}

>>>>

\keywords{
	Exoplanet evolution (491),
  Pre-main sequence stars (1290),
	Stellar rotation (1629),
	Variable stars (1761),
  Low mass stars (2050)
}

@@

With the Gaia astrometry, it has become clear that 25$\,$Ori itself
has distinct subgroups
\citep{kounkel_apogee2_2018,briceno_cidaII_2019}.  In describing the
cluster membership of \ptfo, we follow the notation and results of
\citet{kounkel_apogee2_2018}.  These authors combined astrometric data
from Gaia DR2 with near-infrared spectra from APOGEE-2
\citep{gunn_sdss_2006,majewski_apache_2017,blanton_sloan_2017,zasowski_target_2017,cottle_apogee2_2018}.
They performed a hierarchical clustering on the six-dimensional
position and velocity information to identify subgroups within the
Orion complex.  From smallest to largest, \ptfo\ was identified as a
member of the following hierarchical subgroups:
\begin{equation}
  {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where `$\subset$' means `is a proper subset of'.  25$\,$Ori-1 is the
largest subgroup of 25$\,$Ori, with 149 identified members.  The mean
age of the 25$\,$Ori-1 subgroup, determined by fitting isochrones to
group members with APOGEE effective temperatures and Gaia parallaxes,
was determined to be $8.5\pm1.2\,{\rm Myr}$ \citep[see][Section
2.3]{kounkel_apogee2_2018}.  \citet{kounkel_apogee2_2018} also
identified seven smaller groups in the Orion complex near the Be star
25$\,$Ori. These groups received sequential identifiers, {\it e.g.},
25$\,$Ori-2 (${\rm Age} =12.9\pm2.8\,$Myr; see also
\citealt{briceno_cidaII_2019}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.93\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: The longer-period signal.  {\it Bottom}: The
    shorter-period signal. The phase is defined such that the dip
    occurs at zero phase.  Gray points are the \texttt{PDCSAP} data
    binned to 10-minute cadence.  Black points are binned to 100
    points per period.  The model (blue line) includes 2 harmonics at
    the longer period, plus 3 harmonics and a transit at the shorter
    period.
		\label{fig:phasefold}
	}
\end{figure*}
